Hydra Battles and Cie

### 2021-07-08 doc/part-hydras.tex
update the doc on OrdinalNotations, minor changes

\begin{Coqsrc}
Global Instance Omega : ON  Peano.lt Nat.compare.
Proof.
 split.
 - apply Nat.lt_strorder.
 - apply Wf_nat.lt_wf.
 - apply Nat.compare_spec.
Qed.

@@

Before building an instance of \texttt{ON}, we have to define a comparison function.

@@

@@

\begin{Coqsrc}
Global Instance ON_plus : ON lt compare.
Proof.
  split.
  - apply lt_strorder.
  -  apply lt_wf.
  - apply compare_correct.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition Omega_plus_Omega := ON_plus Omega Omega.

Existing Instance Omega_plus_Omega.
Definition t := @ON_plus.t nat nat.
\end{Coqsrc}

@@

Local Infix "<" := lt.
Local Infix "<=" := (clos_refl _ lt).

@@

Regarding successors, let us introduce the following definition:

@@

Finally, the nature of any ordinal is decidable(inside this notation system) :

>>>>

\begin{Coqsrc}
#[global]
 Instance Omega_comp : Comparable Peano.lt  Nat.compare.
Proof.
  split.
  - apply Nat.lt_strorder.
  - apply Nat.compare_spec.
Qed.

#[global]
 Instance Omega : ON  Peano.lt  Nat.compare.
Proof.
 split.
 - apply Omega_comp.
 - apply Wf_nat.lt_wf.
Qed.

@@

In order to build an instance of \texttt{ON}, we have to define a comparison function.

@@

#[global] Instance plus_comp : Comparable lt compare.
Proof.
  split.
  - apply lt_strorder.
  - apply compare_correct. 
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
#[global] Instance ON_plus : ON lt compare.
Proof.
  split.
  - apply plus_comp.
  - apply lt_wf.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Instance Omega_plus_Omega : ON _ _ := ON_plus Omega Omega.

Definition t := ON_t.
\end{Coqsrc}

@@

  #[local] Infix "<" := lt.
  #[local] Infix "<=" := (leq lt).

@@

Regarding successors, let us define the following function:

@@

Finally, the nature of any ordinal is decidable (inside this notation system) :
